% ============================================================
%  CareerCraft -- Complete Project Documentation
%  Compile with: pdflatex CareerCraft_Documentation.tex
%  (run twice for correct TOC and cross-references)
% ============================================================

\documentclass[12pt, a4paper]{report}

% ── Encoding & fonts ─────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}

% ── Page layout ──────────────────────────────────────────────
\usepackage[
  a4paper,
  top=2.5cm, bottom=2.5cm,
  left=2.5cm, right=2.5cm,
  headheight=15pt
]{geometry}

% ── Colors ───────────────────────────────────────────────────
\usepackage{xcolor}
\definecolor{ccpurple}{RGB}{98,0,238}
\definecolor{ccpurpledk}{RGB}{55,0,179}
\definecolor{ccpurplelt}{RGB}{187,134,252}
\definecolor{ccbg}{RGB}{248,245,255}
\definecolor{codebg}{RGB}{30,30,46}
\definecolor{codefg}{RGB}{205,214,244}
\definecolor{tablerow}{RGB}{245,240,255}
\definecolor{successgr}{RGB}{76,175,80}
\definecolor{warnorange}{RGB}{255,152,0}
\definecolor{infoblue}{RGB}{0,122,204}
\definecolor{graytext}{RGB}{120,120,130}
\definecolor{lightgray}{RGB}{240,240,245}

% ── Hyperlinks ───────────────────────────────────────────────
\usepackage{hyperref}
\hypersetup{
  colorlinks  = true,
  linkcolor   = ccpurple,
  urlcolor    = ccpurpledk,
  citecolor   = ccpurple,
  pdfauthor   = {CareerCraft Development Team},
  pdftitle    = {CareerCraft -- Complete Project Documentation},
  pdfsubject  = {AI-Powered Job Portal},
  bookmarksnumbered = true,
  bookmarksopen     = true,
}

% ── Section headings ─────────────────────────────────────────
\usepackage{titlesec}
\titleformat{\chapter}[display]
  {\normalfont\huge\bfseries\color{ccpurple}}
  {\chaptertitlename\ \thechapter}{12pt}{\Huge}
\titlespacing*{\chapter}{0pt}{20pt}{20pt}

\titleformat{\section}
  {\normalfont\Large\bfseries\color{ccpurpledk}}
  {\thesection}{1em}{}

\titleformat{\subsection}
  {\normalfont\large\bfseries\color{ccpurple!70!black}}
  {\thesubsection}{1em}{}

\titleformat{\subsubsection}
  {\normalfont\normalsize\bfseries\color{graytext}}
  {\thesubsubsection}{1em}{}

% ── Headers & footers ────────────────────────────────────────
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\color{graytext}\small\leftmark}
\fancyhead[R]{\color{graytext}\small CareerCraft Documentation}
\fancyfoot[C]{\color{graytext}\small\thepage}
\renewcommand{\headrulewidth}{0.5pt}

% ── Tables ───────────────────────────────────────────────────
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{array}
\usepackage{multirow}
\usepackage{colortbl}
\renewcommand{\arraystretch}{1.45}

% ── Code listings ────────────────────────────────────────────
\usepackage{listings}

\lstdefinestyle{codestyle}{
  backgroundcolor  = \color{codebg},
  basicstyle       = \ttfamily\small\color{codefg},
  keywordstyle     = \color{ccpurplelt}\bfseries,
  stringstyle      = \color{successgr},
  commentstyle     = \color{graytext}\itshape,
  breaklines       = true,
  breakatwhitespace= true,
  frame            = single,
  framesep         = 5pt,
  framerule        = 0pt,
  showspaces       = false,
  showstringspaces = false,
  tabsize          = 2,
  xleftmargin      = 6pt,
  xrightmargin     = 6pt,
}

\lstdefinestyle{asciistyle}{
  backgroundcolor  = \color{codebg},
  basicstyle       = \ttfamily\footnotesize\color{codefg},
  breaklines       = false,
  frame            = single,
  framesep         = 5pt,
  framerule        = 0pt,
  xleftmargin      = 6pt,
  xrightmargin     = 6pt,
}

\lstdefinestyle{bashstyle}{
  style            = codestyle,
  language         = bash,
  morekeywords     = {flutter,dart,python,npm,pip,git,gcloud,firebase,cd,mkdir},
}

\lstdefinestyle{envstyle}{
  backgroundcolor  = \color{codebg},
  basicstyle       = \ttfamily\small\color{successgr},
  breaklines       = true,
  frame            = single,
  framesep         = 5pt,
  framerule        = 0pt,
  xleftmargin      = 6pt,
  xrightmargin     = 6pt,
}

\lstset{style=codestyle}

% ── Callout boxes ────────────────────────────────────────────
\usepackage[most]{tcolorbox}
\tcbuselibrary{breakable,skins}

\newtcolorbox{tipbox}[1][Tip]{
  enhanced,
  colback   = ccbg,
  colframe  = ccpurple,
  coltitle  = white,
  fonttitle = \bfseries,
  title     = {#1},
  attach boxed title to top left = {yshift=-2.5mm, xshift=4mm},
  boxed title style = {colback=ccpurple, sharp corners, colframe=ccpurpledk},
  breakable,
  before upper = {\parindent0pt},
}

\newtcolorbox{notebox}[1][Note]{
  colback   = infoblue!8!white,
  colframe  = infoblue,
  fonttitle = \bfseries,
  title     = {#1},
  breakable,
  before upper = {\parindent0pt},
}

\newtcolorbox{warningbox}[1][Warning]{
  colback   = warnorange!10!white,
  colframe  = warnorange,
  fonttitle = \bfseries,
  title     = {#1},
  breakable,
  before upper = {\parindent0pt},
}

% ── Lists ────────────────────────────────────────────────────
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*, nosep, topsep=4pt, itemsep=2pt}
\setlist[enumerate]{leftmargin=*, nosep, topsep=4pt, itemsep=2pt}

% ── Spacing ──────────────────────────────────────────────────
\usepackage{parskip}
\setlength{\parskip}{7pt}
\setlength{\parindent}{0pt}

% ── Graphics ─────────────────────────────────────────────────
\usepackage{graphicx}
\usepackage{float}

% ── Custom commands ──────────────────────────────────────────
\newcommand{\cc}{\textit{CareerCraft}}
\newcommand{\code}[1]{\texttt{\small #1}}
\newcommand{\filepath}[1]{\texttt{\small\color{ccpurpledk}#1}}
\newcommand{\method}[1]{\texttt{\textbf{\color{ccpurple}#1}}}
\newcommand{\badge}[2]{%
  \colorbox{#1}{\textcolor{white}{\tiny\bfseries\,#2\,}}%
}
\newcommand{\GET}{\badge{successgr}{GET}}
\newcommand{\POST}{\badge{infoblue}{POST}}
\newcommand{\PATCH}{\badge{warnorange}{PATCH}}
\newcommand{\DELETE}{\badge{red}{DELETE}}

% ── Convenience table column types ───────────────────────────
\newcolumntype{M}[1]{>{\ttfamily\small}p{#1}}   % monospace col
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

% ─────────────────────────────────────────────────────────────
%  DOCUMENT
% ─────────────────────────────────────────────────────────────
\begin{document}

% ── Title page ───────────────────────────────────────────────
\begin{titlepage}
  \pagecolor{ccpurple}
  \color{white}
  \centering
  \vspace*{3cm}

  {\fontsize{58}{66}\selectfont\bfseries CareerCraft}

  \vspace{0.8cm}
  {\LARGE Complete Project Documentation}

  \vspace{0.4cm}
  \textcolor{ccpurplelt}{\large The AI-Powered Job Portal Platform}

  \vspace{2.5cm}

  \begin{tcolorbox}[
    colback  = white!15!ccpurple,
    colframe = white,
    width    = 12cm,
    arc      = 8pt,
    boxrule  = 1pt,
  ]
    \centering\color{white}\small
    Website (Next.js 15)\quad\textbullet\quad Mobile App (Flutter)\\[4pt]
    Browser Extension (Chrome MV3)\quad\textbullet\quad AI Suite (Gemini / GPT-4o / Claude)\\[4pt]
    Backend API (Flask + Python)\quad\textbullet\quad Database (Google Firestore)
  \end{tcolorbox}

  \vfill

  \textcolor{ccpurplelt}{\small Version 1.0\quad\textbullet\quad July 2026}\\[4pt]
  \textcolor{ccpurplelt}{\small\url{https://github.com/Sree8778/CareerCraft}}\\[4pt]
  \textcolor{ccpurplelt}{\small Live demo: \url{https://careercraft-frontend-u7h4zjepfq-uc.a.run.app}}

\end{titlepage}

\nopagecolor
\color{black}

% ── Table of contents ────────────────────────────────────────
\tableofcontents
\clearpage

% ─────────────────────────────────────────────────────────────
\chapter{What is CareerCraft?}
% ─────────────────────────────────────────────────────────────

\cc{} is a \textbf{job portal} --- a website and mobile app that connects people
looking for jobs with companies that want to hire them.

Think of it like a \textbf{Swiss Army knife for job hunting}:
\begin{itemize}
  \item It reads your resume and understands every word of it
  \item It finds matching jobs from many different job websites at once
  \item It applies to those jobs \emph{automatically} on your behalf
  \item It helps you practice for interviews by talking to an AI
  \item It lets recruiters post jobs and manage all their applicants in one place
\end{itemize}

The most important thing that makes \cc{} special: \textbf{all AI features run on
your own free API key} --- you never pay a subscription fee.  Just grab a free key
from Google (takes two minutes) and every AI feature unlocks instantly.

\begin{tipbox}[Free AI Tip]
Google's Gemini AI gives you a generous free tier --- enough for hundreds of AI
operations per month, at zero cost.  No credit card needed.
\end{tipbox}

\section{Real-World Analogy}

Imagine you hired three separate helpers:

\begin{enumerate}
  \item A \textbf{career coach} who rewrites your resume and teaches you to interview
  \item A \textbf{job agent} who searches hundreds of job websites and submits your
        application for you
  \item A \textbf{recruiter's assistant} who reads every application and tells the
        hiring manager which candidates are best
\end{enumerate}

\cc{} is all three of those helpers, in one app, \emph{free}.

\section{How Big Is This Project?}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Metric} & \textbf{Count} \\
\midrule
Backend API endpoints & 50+ \\
Web pages (routes) & 35+ \\
Mobile screens & 27 \\
Database collections & 14 \\
AI features & 18 \\
Lines of code (approx.) & 25{,}000+ \\
Supported AI providers & 5 \\
\bottomrule
\end{tabular}
\end{center}

% ─────────────────────────────────────────────────────────────
\chapter{The Big Picture --- How Everything Fits Together}
% ─────────────────────────────────────────────────────────────

\cc{} is actually \textbf{three products in one}: a website, a mobile app, and a
browser extension.  All three talk to the same backend server and the same database.

\section{Architecture Diagram}

\begin{lstlisting}[style=asciistyle, caption={CareerCraft system architecture}]
+---------------------------------------------------------------+
|                    CAREERCRAFT PLATFORM                       |
|                                                               |
|  +----------------+  +----------------+  +--------------+    |
|  | Website (Web)  |  |  Mobile App    |  |   Browser    |    |
|  | Next.js 15     |  |  Flutter       |  |  Extension   |    |
|  | (React / TS)   |  |  (Android)     |  |  (Chrome)    |    |
|  +-------+--------+  +-------+--------+  +------+-------+    |
|          |                   |                  |            |
|          +-------------------+------------------+            |
|                              |                               |
|               +--------------v--------------+               |
|               |   Backend API  (Flask/Python)|               |
|               |   50+ REST endpoints        |               |
|               |   Cloud Run (Google Cloud)  |               |
|               +--------------+--------------+               |
|                              |                               |
|        +---------------------+---------------------+        |
|        |                     |                     |        |
|  +-----v------+    +---------v------+    +---------v-----+ |
|  |  Firestore  |    | Firebase Auth  |    |  AI Providers | |
|  |  (Database) |    | (Login/Signup) |    |  Gemini/GPT/  | |
|  |  14 colls.  |    |  Email+Google  |    |  Claude/Groq  | |
|  +-------------+    +----------------+    +---------------+ |
+---------------------------------------------------------------+
\end{lstlisting}

\section{What Each Piece Does}

\begin{center}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Piece} & \textbf{Technology} & \textbf{What It Does} \\
\midrule
Website        & Next.js 15 (React)  & The main web app you open in a browser \\
Mobile App     & Flutter (Dart)      & The Android phone app \\
Browser Ext.   & JavaScript (MV3)    & Auto-fills job applications on other sites \\
Backend API    & Flask (Python)      & The ``brain'' --- processes requests, calls AI, talks to DB \\
Database       & Google Firestore    & Stores all users, jobs, messages, applications \\
Auth           & Firebase Auth       & Handles sign-in and sign-out securely \\
AI             & Gemini / GPT / Claude & Powers all smart features using your own key \\
Hosting        & Google Cloud Run    & Runs the app on the internet, auto-scales \\
\bottomrule
\end{tabularx}
\end{center}

\section{How a Request Flows}

Here is exactly what happens when you click ``Enhance this resume bullet point'':

\begin{lstlisting}[style=asciistyle, caption={Request flow for an AI feature}]
[1] You click "Enhance" button in the browser
        |
        v
[2] Browser sends POST /api/enhance-section to Flask backend
    (includes your Firebase ID token as proof you are logged in)
        |
        v
[3] Backend verifies the ID token with Firebase
    --> if invalid: returns 401 Unauthorized (stops here)
        |
        v
[4] Backend reads your API key from Firestore (decrypts it)
        |
        v
[5] Backend sends your text + instructions to Google Gemini
        |
        v
[6] Gemini responds with improved text  (~1-2 seconds)
        |
        v
[7] Backend sends the improved text back as JSON
        |
        v
[8] Browser shows you the improved text on screen
\end{lstlisting}

This entire round trip takes about 1--3 seconds.

% ─────────────────────────────────────────────────────────────
\chapter{Who Uses It? --- The Three Roles}
% ─────────────────────────────────────────────────────────────

When you create an account on \cc{}, you choose one of three roles.
Your role determines which features you see and what you can do.

\section{Candidate (Job Seeker)}

Someone looking for a job.  You upload your resume, \cc{} reads it,
and you get access to all the job-hunting tools.

\textbf{Example:} A college graduate looking for their first engineering job, or a
professional switching careers.

\section{Recruiter (Employer / Hiring Manager)}

Someone posting jobs and reviewing applications.  You post jobs, review candidates,
and manage your hiring pipeline.

\textbf{Example:} An HR manager at a tech company who needs to hire five software
engineers this quarter.

\section{Admin (Super Admin)}

The platform operator.  Admins can turn features on or off for all users, suspend
accounts, and see platform-wide statistics.

\begin{notebox}
Admin access is restricted to specific email addresses set in the backend
configuration.  A regular user cannot become an admin.
\end{notebox}

% ─────────────────────────────────────────────────────────────
\chapter{Features for Job Seekers (Candidates)}
% ─────────────────────────────────────────────────────────────

\section{Dashboard}

The dashboard is the first thing you see after logging in.
It is your job-search command center.

\begin{center}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Widget} & \textbf{What it shows} \\
\midrule
Application Count    & Total number of jobs you have applied to \\
Response Rate        & What percentage of employers replied \\
Interview Rate       & How many interviews you got from your applications \\
Application Funnel   & A chart: Applications $\to$ Responses $\to$ Interviews $\to$ Offers \\
Weekly Activity      & A small graph of your job-search effort over the week \\
AI Insights          & Personalised tips (e.g.\ ``Your resume is missing Python keywords'') \\
Pipeline Stepper     & Where each active application stands right now \\
Profile Strength     & How complete your profile is (shown as a percentage) \\
ATS Score            & How well your resume would pass automated screening (0--100) \\
Recent Applications  & The last few jobs you applied to \\
\bottomrule
\end{tabularx}
\end{center}

\section{Resume Builder}

This is the most powerful feature.  It turns your existing resume into a beautiful,
AI-optimised version.

\subsection{Step 1 --- Upload Your Resume}

Upload a PDF or DOCX file.  The AI reads and extracts all the information
(name, work history, education, skills).  All the fields fill in automatically.

\subsection{Step 2 --- Edit Each Section}

\begin{center}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Section} & \textbf{What goes here} \\
\midrule
Personal Info        & Name, email, phone, location, LinkedIn, GitHub \\
Professional Summary & 2--4 sentences about who you are professionally \\
Work Experience      & Every job: company, title, dates, bullet points \\
Education            & Degrees, schools, graduation years \\
Skills               & Technical and soft skills \\
Certifications       & Licences and certificates you have earned \\
\bottomrule
\end{tabularx}
\end{center}

\subsection{Step 3 --- Use AI Tools}

Every section has an ``Enhance with AI'' button.  The AI rewrites that section to
be more impressive while staying truthful.

\begin{center}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{AI Tool} & \textbf{What it does} \\
\midrule
Enhance Section      & Rewrites a bullet point to sound more impactful \\
Generate Summary     & Creates 3 versions of your professional summary to choose from \\
Elevator Pitch       & Writes a 30-second ``tell me about yourself'' speech \\
Generate Cover Letter & Paste a job posting and get a custom cover letter in seconds \\
Tailor to JD         & Rewrites your resume to include missing keywords from a job ad \\
ATS Score            & Checks if your resume would pass automated screening \\
\bottomrule
\end{tabularx}
\end{center}

\subsection{Step 4 --- Export}

\begin{itemize}
  \item \textbf{Download as PDF} --- best for applying (cannot be easily edited)
  \item \textbf{Download as DOCX} --- best if the employer wants a Word file
\end{itemize}

\subsection{Step 5 --- Save Multiple Versions}

You can save multiple resume versions (e.g.\ ``Resume for Software Engineer'',
``Resume for Product Manager'') and switch between them when applying to
different types of jobs.

\begin{tipbox}[Pro tip]
Tailor your resume to every job you apply to.  The ``Tailor to JD'' feature does
this automatically in about 10 seconds.  A tailored resume is 3$\times$ more
likely to pass ATS screening.
\end{tipbox}

\section{Job Search}

Find jobs using natural language --- like talking to a search engine that actually
understands you.

\textbf{How to use it:}
\begin{enumerate}
  \item Type what you are looking for in plain English:\\
        \emph{``remote React developer job with good work-life balance''}\\
        \emph{``entry level data science role in New York under \$80k''}
  \item The AI reads all available jobs and ranks them by how well they match
  \item Each result shows an \textbf{AI FIT \%} score and a reason why it matches
\end{enumerate}

\textbf{What the results show:}
\begin{itemize}
  \item Job title, company name, location, and job type (Full-time / Remote / Contract)
  \item Salary range (if listed)
  \item An ``AI Fit Reasoning'' box explaining why this job matches your search
  \item An Apply button
\end{itemize}

\section{Smart Apply --- Automated Job Applications}

Instead of applying to one job at a time, Smart Apply searches multiple job boards
simultaneously and applies on your behalf.

\subsection{Job Boards Searched}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Job Board} & \textbf{Website} \\
\midrule
Indeed     & indeed.com \\
LinkedIn   & linkedin.com \\
RemoteOK   & remoteok.com \\
Jobicy     & jobicy.com \\
Arbeitnow  & arbeitnow.com \\
\bottomrule
\end{tabular}
\end{center}

\subsection{How to Use It}

\begin{enumerate}
  \item Type a job title and location (e.g.\ ``Software Engineer, San Francisco'')
  \item The system searches all job boards and shows you matching jobs
  \item Click ``Add to Queue'' on jobs you want to apply to
  \item Choose your mode:
        \begin{itemize}
          \item \textbf{Supervised Mode} --- you review each application before it is sent
          \item \textbf{Autonomous Mode} --- set a daily cap and it applies automatically
        \end{itemize}
  \item Track progress: see which applications were sent, which are pending, and results
\end{enumerate}

\begin{warningbox}[Review your queue first!]
Always review the jobs in your queue before starting autonomous mode.  Once
autonomous apply is running, applications are submitted automatically.
\end{warningbox}

\section{Interview Preparation}

Two ways to practice: AI practice sessions and real scheduled interviews.

\subsection{AI Voice Practice Interview}

Like having a real interviewer to talk to, 24 hours a day, for free.

\textbf{Settings you choose:}
\begin{itemize}
  \item \textbf{Role:} Software Engineer, Product Manager, Marketing, Sales, etc.
  \item \textbf{Interview type:} Behavioural, Technical, Case Study, Mixed
  \item \textbf{Difficulty:} Junior, Mid-level, Senior
\end{itemize}

\textbf{How a session works:}
\begin{enumerate}
  \item The AI asks you a question (you read it or hear it as audio)
  \item You respond by typing or speaking
  \item The AI replies like a real interviewer --- follows up, probes deeper, or moves on
  \item After the session, you get a full report with scores and specific feedback
\end{enumerate}

\subsection{Identity Verification (Proctored Interviews)}

If a company requires proof that you are really you during an interview:
\begin{enumerate}
  \item Upload a photo of your government-issued ID
  \item Take a selfie using your camera
  \item The AI compares the two and gives a similarity score
  \item The result is saved and shared with the recruiter
\end{enumerate}

\subsection{Scheduled Interviews}

When a recruiter books a real interview with you, it appears here.
You can see the date, time, and interviewer's name, get a calendar invite,
and join the video call link when the time comes.

\section{Applications Tracker}

A Kanban board showing all your applications organised by status.

\begin{lstlisting}[style=asciistyle, caption={Applications Kanban board}]
+-------------+  +-------------+  +-------------+  +-------------+
|   APPLIED   |  |  REVIEWED   |  |  INTERVIEW  |  |    OFFER    |
+-------------+  +-------------+  +-------------+  +-------------+
| Google SWE  |  | Meta PM     |  | Apple iOS   |  | Stripe Eng  |
| Amazon SDE  |  | Stripe DS   |  |             |  |             |
| Netflix Eng |  |             |  |             |  |             |
+-------------+  +-------------+  +-------------+  +-------------+
\end{lstlisting}

Click any card to see the full job description and your application materials.

\section{Networking}

Connect with recruiters and other professionals --- like LinkedIn,
but built into \cc{}.

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Tab} & \textbf{What you see} \\
\midrule
Directory  & Everyone on the platform; send a connection request \\
Pending    & Connection requests waiting for your response (accept / decline) \\
Connected  & People you are already connected with \\
\bottomrule
\end{tabular}
\end{center}

\section{Messages}

Real-time chat with recruiters.  When a recruiter wants to discuss your application
informally, they start a conversation here.  You can reply just like a text
message conversation.

\section{Social Feed}

A social-media-style feed where candidates and recruiters share updates, job tips,
and announcements.

\textbf{What you can do:}
\begin{itemize}
  \item Write posts (text)
  \item Like posts from other users
  \item Comment on posts
  \item Delete your own posts
\end{itemize}

\section{Profile}

Your public profile card that recruiters can view.

\begin{center}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Field} & \textbf{What to fill in} \\
\midrule
Full Name          & Your legal full name \\
Professional Title & Your job title (e.g.\ ``Frontend Engineer'') \\
Email \& Phone     & Contact details \\
Location           & City and state \\
LinkedIn           & Your LinkedIn profile URL \\
GitHub             & Your GitHub profile URL (if applicable) \\
Portfolio          & Link to your website or portfolio \\
Profile Photo      & A professional headshot \\
Elevator Pitch     & Auto-generated from your resume \\
\bottomrule
\end{tabularx}
\end{center}

\section{Settings}

\subsection{API Keys --- Bring Your Own Key (BYOK)}

This is how the AI features work at zero cost.  Add one of these free keys:

\begin{center}
\begin{tabular}{lll}
\toprule
\textbf{Provider} & \textbf{How to get a free key} & \textbf{Best for} \\
\midrule
Google Gemini  & aistudio.google.com     & Everything (recommended) \\
OpenAI GPT-4o  & platform.openai.com     & Resume writing \\
Anthropic Claude & console.anthropic.com & Analysis \& reasoning \\
Groq (Llama 3) & console.groq.com        & Fast responses \\
NVIDIA NIM     & build.nvidia.com        & High-performance tasks \\
\bottomrule
\end{tabular}
\end{center}

You can add multiple keys.  If one runs out of credits, \cc{} automatically
switches to the next one.

\subsection{Other Settings}

\begin{itemize}
  \item Dark / Light theme toggle
  \item Email notification preferences
  \item Two-factor authentication (extra security)
\end{itemize}

% ─────────────────────────────────────────────────────────────
\chapter{Features for Recruiters}
% ─────────────────────────────────────────────────────────────

\section{Dashboard}

Shows hiring performance at a glance.

\begin{center}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Metric} & \textbf{What it means} \\
\midrule
Open Jobs           & Number of active job postings you have live \\
Total Applications  & Incoming applications across all your jobs \\
Interview Rate      & Percentage of applicants who reached the interview stage \\
Recent Applications & The latest applications that just came in \\
\bottomrule
\end{tabularx}
\end{center}

\section{Post a Job (Requisitions)}

A four-step wizard that makes posting a job fast and easy.

\subsection{Step 1 --- Role Details}
\begin{itemize}
  \item Job title, department, location (city / remote / hybrid)
  \item Employment type: Full-time, Part-time, Contract, Internship
  \item Salary range
\end{itemize}

\subsection{Step 2 --- AI-Generated Job Description}
Click ``Generate with AI'' and get a complete, professional job description in
seconds.  You can edit any part of it.

\subsection{Step 3 --- Screening Questions}
Add custom questions candidates must answer:
\begin{itemize}
  \item \textbf{Multiple choice} --- e.g.\ ``Are you authorised to work in the US?''
  \item \textbf{Open text} --- e.g.\ ``Describe a challenging technical problem you solved''
  \item \textbf{Knockout questions} --- if a candidate answers wrong, they are automatically
        rejected\\
        \textit{Example: ``Do you have 3+ years of Python? (Required)'' --- a ``No'' answer
        instantly rejects the applicant}
\end{itemize}

\subsection{Step 4 --- Preview \& Publish}
Review how the job posting looks, then click Publish.  It goes live immediately.

\section{Application Pipeline}

A Kanban board showing all applications for all your jobs, organised by status.

\begin{center}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Action} & \textbf{How to do it} \\
\midrule
View resume         & Click any applicant card \\
See AI Fit Score    & Shown on each card (0--100\%) \\
See ATS Score       & Shown on the application detail page \\
Move to next stage  & Drag the card or use the status dropdown \\
Schedule interview  & Click ``Schedule Interview'' on the detail page \\
Send rejection      & Click ``Reject'' --- uses a professional email template \\
Make offer          & Click ``Make Offer'' --- opens an offer form \\
\bottomrule
\end{tabularx}
\end{center}

\section{AI Fit Analysis}

Click ``Analyse Fit'' on any application to get:
\begin{itemize}
  \item An overall match percentage
  \item Which requirements the candidate meets and which they are missing
  \item Keyword gaps --- important skills from your job description missing from their resume
  \item A recommendation: \textbf{Strong Match}, \textbf{Possible Match}, or \textbf{Not a Match}
\end{itemize}

\section{Candidate Directory \& AI Copilot Search}

A searchable database of all candidates on the platform.

\begin{itemize}
  \item \textbf{Standard search:} type a skill or job title
  \item \textbf{AI Copilot Search:} type in plain English\\
        \textit{``experienced backend developer who has worked at startups and knows Kubernetes''}
\end{itemize}

Click any candidate to see their full profile, resume, and skills.

\section{Webhooks --- ATS Integration}

If your company already uses a separate Applicant Tracking System (Greenhouse,
Workday, Lever, etc.), you can connect it to \cc{} using webhooks.

Every time something happens in \cc{} (new application, status change, interview
booked), a notification is automatically sent to your ATS so everything stays in sync.

\textbf{Setup:}
\begin{enumerate}
  \item Go to Settings $\to$ Webhooks
  \item Paste your ATS webhook URL
  \item Click ``Test Ping'' to verify the connection works
  \item Save --- \cc{} will now notify your ATS automatically
\end{enumerate}

% ─────────────────────────────────────────────────────────────
\chapter{Features for Admins}
% ─────────────────────────────────────────────────────────────

Admins access the admin panel at \code{/admin}.
This is only visible to email addresses pre-approved in the backend configuration.

\section{Feature Flags}

Turn platform features on or off with a single toggle.  Useful for rolling out
new features gradually or disabling features during maintenance.

\begin{center}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Flag name} & \textbf{What it controls} \\
\midrule
\code{feed}         & The social feed page \\
\code{smartApply}   & Automated job applications \\
\code{aiInterview}  & AI voice interview practice \\
\code{practiceMode} & Interview practice sessions \\
\code{resumeBuilder}& Resume builder tool \\
\code{network}      & Connections and networking \\
\code{messages}     & Direct messaging \\
\code{sourcing}     & Passive talent sourcing \\
\code{webhooks}     & ATS integrations \\
\code{companies}    & Company directory and reviews \\
\code{signups}      & New user registrations (turn off for private beta) \\
\bottomrule
\end{tabularx}
\end{center}

\section{User Management}

\begin{itemize}
  \item View all users: name, email, role, join date, suspension status
  \item \textbf{Suspend account} --- the user is immediately signed out and cannot log in
  \item \textbf{Reinstate account} --- restore access to a suspended user
\end{itemize}

\section{Job Moderation}

View all job postings on the platform and remove inappropriate or spammy jobs.

\section{Platform Statistics}

\begin{itemize}
  \item Total users (candidates vs.\ recruiters)
  \item Total jobs posted
  \item Total applications submitted
  \item Platform growth over time
\end{itemize}

% ─────────────────────────────────────────────────────────────
\chapter{The Chrome Browser Extension}
% ─────────────────────────────────────────────────────────────

The browser extension is a small tool you install in Chrome.  It lives in your
toolbar and auto-fills job application forms on other websites --- so you do not
have to type your name, email, and resume information a hundred times.

\section{How to Install}

\begin{enumerate}
  \item Open Chrome and go to \code{chrome://extensions}
  \item Turn on \textbf{Developer Mode} (toggle in the top-right corner)
  \item Click \textbf{Load unpacked}
  \item Navigate to the \filepath{web/browser-extension/} folder and select it
  \item The CareerCraft icon appears in your Chrome toolbar
\end{enumerate}

\section{How to Use It}

\begin{enumerate}
  \item Go to any job application page (Indeed, Greenhouse, Lever, Workday, etc.)
  \item Click the CareerCraft icon in your toolbar
  \item The popup shows your profile, a resume selector dropdown, and an Autofill button
  \item Click \textbf{``Autofill Application''}
  \item Watch as every field fills in automatically
\end{enumerate}

\subsection{Fields Filled Automatically}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Field} & \textbf{Data source} \\
\midrule
First name, Last name & Your profile name (split correctly) \\
Email address         & Your profile email \\
Phone number          & Your profile phone \\
LinkedIn URL          & Your profile LinkedIn link \\
GitHub URL            & Your profile GitHub link \\
Portfolio URL         & Your profile website \\
Address, City, State, ZIP & Your profile location \\
Work authorisation    & Answered from profile \\
\bottomrule
\end{tabular}
\end{center}

\section{How the Autofill Works (Simplified)}

The extension is smart about reading forms.  It does not just look at field
names --- it reads the \textbf{labels} near each field to understand what that
field is asking for.

For example, if a form has a label that says ``Legal First Name'' followed by a
text box, the extension knows to put your first name in that box --- even though
the field itself is not labelled \code{firstName}.  This is called
\textbf{label-based haystack detection} and it works on virtually any job
application form.

\section{Handling Custom Screening Questions}

For open-text questions like ``Tell us about a challenge you overcame'',
the extension sends the question to your AI and fills in a relevant answer
drawn from your resume.

\begin{warningbox}[Always review before submitting]
AI-generated answers to custom questions are a starting point, not a final
answer.  Always read and edit them before clicking Submit on the job site.
\end{warningbox}

\section{Resume Selection}

If you have saved multiple resume versions in the \cc{} resume builder, you can
pick which one to use for this application using the dropdown in the extension
popup.  The extension fetches the selected resume's data from the backend and
uses it for the autofill.

% ─────────────────────────────────────────────────────────────
\chapter{The Mobile App}
% ─────────────────────────────────────────────────────────────

The mobile app (Android) gives you access to \cc{} from your phone.  It has
nearly all the same features as the website and connects to the exact same
backend and database.

\section{How to Install}

\subsection{Option A --- Direct APK (current method)}
\begin{enumerate}
  \item Enable ``Install from unknown sources'' on your phone
        (Settings $\to$ Security $\to$ Install unknown apps)
  \item Transfer the APK file to your phone
  \item Open the APK file on your phone and follow the prompts
\end{enumerate}

\subsection{Option B --- Build from Source}
\begin{lstlisting}[style=bashstyle]
# In the mobile/ folder:
flutter build apk --release

# Install on a connected device:
flutter install --device-id YOUR_DEVICE_ID
\end{lstlisting}

\section{How to Log In}

\begin{itemize}
  \item \textbf{Email \& Password:} same account you use on the website
  \item \textbf{Google Sign-In:} tap ``Continue with Google'' to use your Google account
\end{itemize}

All your data (jobs, messages, applications) is shared in real-time between
the website and the mobile app.

\section{Mobile Screens}

\begin{center}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Screen} & \textbf{What it does} \\
\midrule
Home                & Choose role (Candidate or Recruiter) \\
Candidate Dashboard & Stats, quick actions, notifications \\
Job Search          & Browse and search jobs, view details, apply \\
Smart Apply         & Automated applications on mobile \\
Resume Builder      & Edit resume, use AI tools on mobile \\
Applications        & Track your application status \\
Interview           & Practice interviews and schedule real ones \\
Messages            & Chat with recruiters \\
Network             & Connections directory \\
Social Feed         & Post and interact with the community \\
Companies           & Company directory and reviews \\
Recruiter Dashboard & KPIs and hiring overview \\
Post a Job          & Create a new job posting \\
Application Pipeline& Review incoming applications \\
Candidate Directory & Search all candidates \\
Candidate Detail    & View a candidate's full resume \\
Recruiter Messages  & Chat with applicants \\
Webhooks            & ATS integration management \\
Profile             & Edit your profile \\
More / Settings     & Logout, theme, account settings \\
\bottomrule
\end{tabularx}
\end{center}

% ─────────────────────────────────────────────────────────────
\chapter{How the AI Works}
% ─────────────────────────────────────────────────────────────

\section{The Bring Your Own Key (BYOK) System}

\cc{} does not pay for AI on your behalf.  Instead, you add your own free API
key from one of the supported AI providers, and \cc{} uses it to power all
smart features.

\begin{notebox}[Why BYOK is better for you]
\begin{itemize}
  \item Google Gemini gives you a generous free tier (hundreds of uses per month, no card required)
  \item You pay no subscription fee to CareerCraft
  \item Your data goes directly from CareerCraft to the AI provider --- it is never sold or used for training
\end{itemize}
\end{notebox}

\subsection{How to Get a Free Gemini Key}
\begin{enumerate}
  \item Go to \url{https://aistudio.google.com}
  \item Click ``Get API key'' $\to$ ``Create API key''
  \item Copy the key
  \item In \cc{}: Settings $\to$ API Keys $\to$ Add Key $\to$ paste $\to$ Save
\end{enumerate}

\section{The AI Key Router}

If you add multiple API keys, the \textbf{AI Router} uses them intelligently:
\begin{enumerate}
  \item Tries keys in the order you added them
  \item If a key hits its rate limit or returns an error, it silently switches to the next key
  \item You never see an error because of an exhausted key
\end{enumerate}

\section{Key Encryption}

Your API keys are stored in the database \textbf{encrypted} --- turned into
scrambled text that can only be decoded by the backend server.  Even if someone
gained access to the database, they could not read your keys.

The method used is \textbf{Fernet} symmetric encryption.  The master decryption
key exists only as a server-side environment variable, never in any code file.

\section{AI Features Reference}

\begin{center}
{\small
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Feature} & \textbf{What the AI actually does} \\
\midrule
Parse Resume         & Reads a PDF and extracts structured data (name, jobs, education) \\
Enhance Section      & Rewrites a resume bullet to be more impact-focused \\
Generate Summary     & Writes 3 professional summary options from your career history \\
Elevator Pitch       & Writes a conversational 30-second intro \\
Cover Letter         & Matches your skills to a job description and writes a letter \\
Tailor to JD         & Rewrites your resume using keywords from a specific job posting \\
ATS Score            & Evaluates formatting, keywords, and length (0--100 score) \\
Practice Interview   & Generates questions, evaluates your answers, gives feedback \\
Semantic Job Search  & Understands what you want from a plain-English description \\
Fit Analysis         & Compares a candidate's resume to a job description (recruiter tool) \\
AI Copilot Search    & Finds matching candidates from a plain-English query (recruiter) \\
Generate Job Desc.   & Writes a full job posting from a title and requirements \\
Solve Custom Qs      & Answers application screening questions using your resume \\
Voice Evaluation     & Grades a spoken interview answer on grammar, confidence, relevance \\
\bottomrule
\end{tabularx}
}
\end{center}

% ─────────────────────────────────────────────────────────────
\chapter{The Database}
% ─────────────────────────────────────────────────────────────

\cc{} uses \textbf{Google Firestore} --- a cloud database that stores data as
collections of documents (like folders of JSON files).

\section{Database Collections}

\begin{center}
{\small
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Collection} & \textbf{Who can access} & \textbf{What is stored} \\
\midrule
\code{users}            & Owner only           & Name, email, role, avatar, profile info, suspension flag \\
\code{resumes}          & Owner only           & Resume data, saved versions, file upload info \\
\code{resumeDrafts}     & Owner only           & Auto-saved drafts from the resume builder \\
\code{apiKeysWallet}    & Owner reads; backend writes & Encrypted API keys list \\
\code{jobs}             & All logged-in users  & Job postings: title, company, description, requirements, salary \\
\code{scraped\_jobs}    & All logged-in users  & Jobs crawled from external boards (Indeed, LinkedIn, etc.) \\
\code{applications}     & Backend only         & Applications: candidateId, jobId, status, resume, answers \\
\code{interviews}       & Authenticated users  & Interview sessions and AI feedback \\
\code{chats}            & Backend only         & Chat thread metadata (participants, last message) \\
\code{conversations}    & Participants only    & Individual messages within a chat \\
\code{connections}      & Backend only         & Connection requests: senderId, receiverId, status \\
\code{notifications}    & Recipient only       & Platform alerts: new application, message, etc. \\
\code{apply\_sessions}  & Backend only         & Autonomous apply session state \\
\bottomrule
\end{tabularx}
}
\end{center}

\section{Real-Time Updates}

Firestore updates in real time.  When a recruiter sends you a message, it
appears in your chat window within 1--2 seconds without you needing to refresh
the page.  This is because the app ``listens'' to the database for changes and
updates the screen automatically.

% ─────────────────────────────────────────────────────────────
\chapter{Security}
% ─────────────────────────────────────────────────────────────

\section{How Login Works}

\begin{enumerate}
  \item You enter your email and password
  \item Firebase Authentication checks if they are correct
  \item Firebase issues an \textbf{ID token} --- a long string that acts like a
        temporary badge
  \item Every request to the backend includes this token in the header:\\
        \code{Authorization: Bearer \textless{}token\textgreater{}}
  \item The backend verifies the token with Firebase before doing anything
  \item Tokens expire after 1 hour but are silently refreshed so you stay logged in
\end{enumerate}

\section{Two-Factor Authentication (2FA)}

An optional extra layer of security:
\begin{enumerate}
  \item Settings $\to$ Security $\to$ Enable 2FA
  \item Enter your email or phone number
  \item Every subsequent login requires both your password and a 6-digit code
\end{enumerate}

\section{What CareerCraft Can Never See}

\begin{itemize}
  \item Your plain-text API keys (they are encrypted before storage)
  \item Your Firebase password (Firebase handles authentication --- \cc{} never touches it)
\end{itemize}

\section{Account Suspension}

If an admin suspects an account is being misused:
\begin{enumerate}
  \item Admin clicks ``Suspend'' in the admin panel
  \item The \code{suspended: true} flag is set on the user's Firestore document
  \item The user is immediately signed out
  \item On their next login attempt they receive an error message
\end{enumerate}

% ─────────────────────────────────────────────────────────────
\chapter{Setting Up the Project}
% ─────────────────────────────────────────────────────────────

This chapter is for developers who want to run \cc{} on their own computer.

\section{Prerequisites}

\begin{center}
\begin{tabular}{lll}
\toprule
\textbf{Tool} & \textbf{Version} & \textbf{Where to install} \\
\midrule
Node.js  & 18 or higher & \url{https://nodejs.org} \\
Python   & 3.11 or higher & \url{https://python.org} \\
Flutter  & 3.24 or higher & \url{https://flutter.dev} \\
Git      & any recent & \url{https://git-scm.com} \\
gcloud CLI & any recent & cloud.google.com/sdk \\
\bottomrule
\end{tabular}
\end{center}

\section{Step 1 --- Clone the Repository}

\begin{lstlisting}[style=bashstyle]
git clone https://github.com/Sree8778/CareerCraft.git
cd CareerCraft
\end{lstlisting}

\section{Step 2 --- Set Up Firebase}

\begin{enumerate}
  \item Go to \url{https://console.firebase.google.com}
  \item Create a new project (or use \code{recruit-edge-e0d1b})
  \item Enable \textbf{Authentication} $\to$ sign-in methods: Email/Password and Google
  \item Enable \textbf{Firestore Database} $\to$ start in test mode
  \item Project Settings $\to$ Service Accounts $\to$ Generate new private key
  \item Save the JSON file as \filepath{web/backend/credentials/firebase-adminsdk.json}
  \item Project Settings $\to$ General $\to$ copy your web app config
  \item Create \filepath{web/.env.local}:
\end{enumerate}

\begin{lstlisting}[style=envstyle]
NEXT_PUBLIC_FIREBASE_API_KEY=your_api_key
NEXT_PUBLIC_FIREBASE_AUTH_DOMAIN=your_project.firebaseapp.com
NEXT_PUBLIC_FIREBASE_PROJECT_ID=your_project_id
NEXT_PUBLIC_FIREBASE_STORAGE_BUCKET=your_project.appspot.com
NEXT_PUBLIC_FIREBASE_MESSAGING_SENDER_ID=your_sender_id
NEXT_PUBLIC_FIREBASE_APP_ID=your_app_id
NEXT_PUBLIC_API_URL=http://localhost:5000/api
\end{lstlisting}

\section{Step 3 --- Set Up the Backend}

\begin{lstlisting}[style=bashstyle]
cd web/backend

# Create an isolated Python environment
python -m venv venv

# Activate it (Windows)
venv\Scripts\activate

# Install all Python packages
pip install -r requirements.txt
\end{lstlisting}

Create \filepath{web/backend/.env}:

\begin{lstlisting}[style=envstyle]
GEMINI_API_KEY=your_gemini_key
# Generate vault key with:
# python -c "from cryptography.fernet import Fernet; print(Fernet.generate_key().decode())"
BACKEND_VAULT_MASTER_KEY=your_generated_fernet_key
\end{lstlisting}

Start the backend:

\begin{lstlisting}[style=bashstyle]
python app.py
# Server starts at http://localhost:5000
\end{lstlisting}

\section{Step 4 --- Set Up the Frontend}

\begin{lstlisting}[style=bashstyle]
cd web
npm install        # install dependencies
npm run dev        # start development server at http://localhost:3000
\end{lstlisting}

\section{Step 5 --- Set Up the Mobile App (Optional)}

\begin{lstlisting}[style=bashstyle]
cd mobile
flutter pub get    # download Flutter packages
flutter run        # launch on connected device or emulator
\end{lstlisting}

\section{Step 6 --- Install the Browser Extension (Optional)}

\begin{enumerate}
  \item Open Chrome $\to$ \code{chrome://extensions}
  \item Enable \textbf{Developer Mode} (top-right toggle)
  \item Click \textbf{Load unpacked}
  \item Select the \filepath{web/browser-extension/} folder
  \item Extension is installed
\end{enumerate}

% ─────────────────────────────────────────────────────────────
\chapter{Deploying to the Internet}
% ─────────────────────────────────────────────────────────────

\cc{} runs on \textbf{Google Cloud Run} --- a service that automatically scales
up when many people use it and scales down when they do not, so you only pay
for actual usage.

\section{The \texttt{.env.cloud} File}

Create this file at the project root.  It is gitignored --- \textbf{never commit it}.

\begin{lstlisting}[style=envstyle]
GCP_PROJECT_ID=recruit-edge-e0d1b
GCP_REGION=us-central1
GEMINI_API_KEY=your_gemini_key
BACKEND_VAULT_MASTER_KEY=your_fernet_key
RESEND_API_KEY=your_resend_key
EMAIL_FROM=noreply@careercraft.app
PLATFORM_URL=https://careercraft-frontend-u7h4zjepfq-uc.a.run.app
NEXT_PUBLIC_FIREBASE_API_KEY=your_firebase_key
NEXT_PUBLIC_FIREBASE_AUTH_DOMAIN=recruit-edge-e0d1b.firebaseapp.com
NEXT_PUBLIC_FIREBASE_PROJECT_ID=recruit-edge-e0d1b
NEXT_PUBLIC_FIREBASE_STORAGE_BUCKET=recruit-edge-e0d1b.appspot.com
NEXT_PUBLIC_FIREBASE_MESSAGING_SENDER_ID=414523842687
NEXT_PUBLIC_FIREBASE_APP_ID=your_app_id
\end{lstlisting}

\section{Deploy Everything (Frontend + Backend)}

\begin{lstlisting}[style=bashstyle]
.\deploy.ps1
\end{lstlisting}

This script does the following automatically:
\begin{enumerate}
  \item Reads all secrets from \filepath{.env.cloud}
  \item Enables required Google Cloud APIs
  \item Builds the backend Docker image via Cloud Build
  \item Deploys the backend to Cloud Run
  \item Builds the frontend Docker image with the backend URL baked in
  \item Deploys the frontend to Cloud Run
  \item Prints the live URLs when done
\end{enumerate}

\section{Deploy Frontend Only (Faster)}

\begin{lstlisting}[style=bashstyle]
.\deploy.ps1 -FrontendOnly
\end{lstlisting}

Use this when you only changed frontend code.  Skips the backend build (saves $\approx$5 minutes).

\section{After Deploying}

\begin{enumerate}
  \item Add the new frontend URL to Firebase Console $\to$ Authentication $\to$ Authorized domains
  \item Deploy Firestore security rules: \code{firebase deploy --only firestore:rules}
  \item Visit the frontend URL and verify everything works
\end{enumerate}

\section{Current Live URLs}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Service} & \textbf{URL} \\
\midrule
Frontend & \small\url{https://careercraft-frontend-u7h4zjepfq-uc.a.run.app} \\
Backend API & \small\url{https://careercraft-backend-u7h4zjepfq-uc.a.run.app/api} \\
\bottomrule
\end{tabular}
\end{center}

% ─────────────────────────────────────────────────────────────
\chapter{Full API Reference}
% ─────────────────────────────────────────────────────────────

Every endpoint the backend exposes.  All authenticated endpoints require the
header:\\[4pt]
\code{Authorization: Bearer \{firebase\_id\_token\}}

\textbf{Key:} \GET\ = read data\quad \POST\ = create/action\quad
\PATCH\ = update\quad \DELETE\ = remove

{\small\setlength{\tabcolsep}{4pt}

% ── Authentication ───────────────────────────────────────────
\section{Authentication}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\POST & \code{/auth/send-email-otp} & Anyone & Send a one-time password to an email address \\
\POST & \code{/auth/verify-email-otp} & Anyone & Verify the OTP code entered by user \\
\POST & \code{/auth/2fa/setup} & Logged-in user & Set up two-factor authentication \\
\POST & \code{/auth/2fa/verify} & Anyone & Verify 2FA code during login \\
\POST & \code{/auth/2fa/disable} & Logged-in user & Turn off 2FA \\
\bottomrule
\end{longtable}

% ── Users ────────────────────────────────────────────────────
\section{Users}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\POST  & \code{/users/register}         & Anyone  & Create a new user account \\
\GET   & \code{/users}                  & Admin   & Get all users on the platform \\
\PATCH & \code{/users/\{uid\}/profile}  & Owner   & Update name, email, phone, location \\
\GET   & \code{/users/\{uid\}/completion}& Owner  & Get profile completion \% and missing fields \\
\GET   & \code{/stats/candidate/\{uid\}}& Owner   & Candidate dashboard statistics \\
\GET   & \code{/stats/recruiter/\{uid\}}& Owner   & Recruiter dashboard statistics \\
\bottomrule
\end{longtable}

% ── Jobs ─────────────────────────────────────────────────────
\section{Jobs}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\GET   & \code{/jobs}                          & Logged in  & List all job postings \\
\POST  & \code{/jobs/v1/post}                  & Recruiter  & Create a new job posting \\
\GET   & \code{/jobs/\{job\_id\}}              & Logged in  & Get one job's full details \\
\PATCH & \code{/jobs/\{job\_id\}}              & Job owner  & Edit a job posting \\
\POST  & \code{/jobs/\{job\_id\}/apply}        & Candidate  & Submit a job application \\
\GET   & \code{/jobs/\{job\_id\}/applications} & Recruiter  & List all applications for this job \\
\POST  & \code{/jobs/search-semantic}           & Logged in  & Search jobs in natural language \\
\POST  & \code{/jobs/generate-description}      & Recruiter  & AI-generate a job description \\
\POST  & \code{/jobs/crawl}                    & Recruiter  & Scrape external job boards \\
\bottomrule
\end{longtable}

% ── Applications ─────────────────────────────────────────────
\section{Applications}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\GET  & \code{/applications}                      & Both       & List applications (filtered by role) \\
\GET  & \code{/applications/\{app\_id\}}          & Participant& Get one application's full details \\
\POST & \code{/applications/\{app\_id\}/status}   & Recruiter  & Update application status \\
\POST & \code{/applications/\{app\_id\}/ai-screen}& Recruiter  & Run AI screening analysis \\
\POST & \code{/applications/\{app\_id\}/ats-score}& Recruiter  & Calculate ATS score \\
\bottomrule
\end{longtable}

% ── Resume Tools ─────────────────────────────────────────────
\section{Resume Tools}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\POST & \code{/parse-resume}               & Candidate & Upload PDF/DOCX, get structured JSON \\
\POST & \code{/generate-pdf}               & Candidate & Export resume JSON to a PDF file \\
\POST & \code{/generate-docx}              & Candidate & Export resume JSON to a Word file \\
\POST & \code{/resume/analyze}             & Candidate & Detailed ATS and format analysis \\
\POST & \code{/generate-elevator-pitch}    & Candidate & Write a 30-second professional pitch \\
\POST & \code{/enhance-section}            & Candidate & AI-rewrite a specific resume section \\
\POST & \code{/generate-summary-suggestions}& Candidate& Get 3 professional summary options \\
\POST & \code{/generate-cover-letter}      & Candidate & Write a custom cover letter \\
\POST & \code{/grade-resume}               & Candidate & Score resume vs.\ a job description \\
\POST & \code{/resume/tailor-to-jd}        & Candidate & Rewrite resume using a job's keywords \\
\bottomrule
\end{longtable}

% ── Interviews ───────────────────────────────────────────────
\section{Interviews}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\GET  & \code{/interviews}                       & Both      & List all interviews \\
\POST & \code{/interviews/schedule}              & Recruiter & Book an interview with a candidate \\
\POST & \code{/interviews/verify-identity}       & Candidate & Submit ID + selfie for identity check \\
\POST & \code{/interviews/get-next-question}     & Candidate & Get next dynamic interview question \\
\POST & \code{/interviews/evaluate-response}     & Candidate & Grade a spoken response \\
\POST & \code{/practice-interview/question}      & Candidate & Get a practice question \\
\POST & \code{/practice-interview/ai-turn}       & Candidate & Get AI interviewer's next message \\
\POST & \code{/practice-interview/evaluate}      & Candidate & Score your answer to a question \\
\POST & \code{/practice-interview/final-feedback}& Candidate & Get end-of-session full report \\
\bottomrule
\end{longtable}

% ── Candidates (recruiter tools) ─────────────────────────────
\section{Candidates (Recruiter Tools)}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\GET  & \code{/candidates}                & Recruiter & List all candidates \\
\GET  & \code{/candidates/\{uid\}/resume} & Recruiter & Fetch a candidate's resume \\
\POST & \code{/candidates/search-copilot} & Recruiter & Natural-language candidate search \\
\POST & \code{/analyze-fit}               & Recruiter & Score a candidate vs.\ job description \\
\bottomrule
\end{longtable}

% ── Smart Apply ──────────────────────────────────────────────
\section{Smart Apply}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\POST & \code{/smart-apply/search}             & Candidate & Search multiple job boards at once \\
\POST & \code{/smart-apply/queue/add}          & Candidate & Add a job to the apply queue \\
\POST & \code{/smart-apply/queue/remove}       & Candidate & Remove a job from the queue \\
\GET  & \code{/smart-apply/queue}              & Candidate & View the current apply queue \\
\POST & \code{/smart-apply/apply-supervised}   & Candidate & Apply to one job (with review) \\
\POST & \code{/smart-apply/autonomous/start}   & Candidate & Start bulk auto-apply \\
\POST & \code{/smart-apply/autonomous/stop}    & Candidate & Stop auto-apply session \\
\GET  & \code{/smart-apply/status}             & Candidate & Check current apply progress \\
\bottomrule
\end{longtable}

% ── Messaging & Networking ───────────────────────────────────
\section{Messaging \& Networking}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\GET    & \code{/chats}                          & Both        & List all your conversations \\
\POST   & \code{/chats}                          & Both        & Start a new conversation \\
\GET    & \code{/chats/\{chat\_id\}/messages}    & Participant & Get messages in a conversation \\
\POST   & \code{/chats/\{chat\_id\}/messages}    & Participant & Send a message \\
\GET    & \code{/connections}                    & Both        & List your connections \\
\POST   & \code{/connections/request}            & Both        & Send a connection request \\
\POST   & \code{/connections/\{id\}/respond}     & Recipient   & Accept or decline a request \\
\GET    & \code{/feed}                           & Both        & Get social feed posts \\
\POST   & \code{/posts}                          & Both        & Create a new post \\
\POST   & \code{/posts/\{post\_id\}/like}        & Both        & Like a post \\
\POST   & \code{/posts/\{post\_id\}/comments}    & Both        & Comment on a post \\
\DELETE & \code{/posts/\{post\_id\}}             & Author      & Delete your own post \\
\bottomrule
\end{longtable}

% ── API Keys / Vault ─────────────────────────────────────────
\section{API Keys \& Vault}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\POST & \code{/vault/verify-key}     & Owner & Test whether an API key is valid \\
\POST & \code{/vault/wallet/stack}   & Owner & Add a new key to your key wallet \\
\GET  & \code{/vault/wallet/status}  & Owner & Check key status and remaining quota \\
\POST & \code{/vault/wallet/remove}  & Owner & Remove a key from your wallet \\
\bottomrule
\end{longtable}

% ── Browser Extension ────────────────────────────────────────
\section{Browser Extension Endpoints}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.5cm}p{5.2cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Auth type} & \textbf{What it does} \\
\midrule
\endhead
\POST & \code{/plugin/token}   & Firebase token  & Get a long-lived plugin token \\
\GET  & \code{/plugin/profile} & Plugin token    & Get profile data for autofill \\
\GET  & \code{/plugin/resumes} & Plugin token    & List saved resume versions \\
\POST & \code{/plugin/applied} & Plugin token    & Log a completed application \\
\bottomrule
\end{longtable}

% ── Notifications ────────────────────────────────────────────
\section{Notifications}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\GET  & \code{/notifications}          & Both & Get your notifications \\
\POST & \code{/notifications/read-all} & Both & Mark all notifications as read \\
\bottomrule
\end{longtable}

% ── Webhooks ─────────────────────────────────────────────────
\section{Webhooks}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\GET  & \code{/webhooks/subscriptions} & Recruiter & List all webhook subscriptions \\
\POST & \code{/webhooks/subscribe}     & Recruiter & Add a new webhook endpoint \\
\POST & \code{/webhooks/test-ping}     & Recruiter & Send a test payload to a URL \\
\bottomrule
\end{longtable}

% ── Companies ────────────────────────────────────────────────
\section{Companies}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\GET  & \code{/companies}                     & Anyone    & List companies (with optional search) \\
\GET  & \code{/companies/\{id\}}              & Anyone    & Get one company's details \\
\GET  & \code{/companies/\{id\}/reviews}      & Anyone    & Get employee reviews \\
\POST & \code{/companies/\{id\}/reviews}      & Candidate & Submit an employee review \\
\GET  & \code{/companies/\{id\}/qna}          & Anyone    & Get company Q\&A thread \\
\POST & \code{/companies/\{id\}/qna}          & Both      & Post a question or answer \\
\bottomrule
\end{longtable}

% ── Admin ────────────────────────────────────────────────────
\section{Admin}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\GET  & \code{/admin/me}                     & Admin & Confirm you have admin access \\
\GET  & \code{/admin/stats}                  & Admin & Platform-wide statistics \\
\GET  & \code{/admin/users}                  & Admin & All users with their stats \\
\POST & \code{/admin/users/\{uid\}/suspend}  & Admin & Suspend a user account \\
\GET  & \code{/admin/jobs}                   & Admin & All jobs (for moderation) \\
\PUT  & \code{/admin/features}               & Admin & Toggle feature flags on/off \\
\bottomrule
\end{longtable}

% ── Platform ─────────────────────────────────────────────────
\section{Platform \& Public}

\begin{longtable}{p{1.5cm}p{5.5cm}p{2.2cm}p{5.5cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Who} & \textbf{What it does} \\
\midrule
\endhead
\GET & \code{/platform/config}    & Anyone & Get feature flags and public config \\
\GET & \code{/benefits}           & Anyone & Public employee benefits directory \\
\GET & \code{/testimonials}       & Anyone & User success stories \\
\GET & \code{/employers/featured} & Anyone & Featured employer showcase \\
\GET & \code{/stats/salaries}     & Anyone & Crowdsourced salary data \\
\bottomrule
\end{longtable}

} % end \small

% ─────────────────────────────────────────────────────────────
\chapter{Folder Structure}
% ─────────────────────────────────────────────────────────────

Every important file and folder in the project, with a description.

\begin{lstlisting}[style=asciistyle, caption={Complete project folder structure}]
CareerCraft/
|
+-- web/                              <- The website
|   +-- src/
|   |   +-- app/                      <- Every page of the website
|   |   |   +-- page.tsx              <- Home / landing page
|   |   |   +-- feed/page.tsx         <- Social feed
|   |   |   +-- signup/page.tsx       <- Sign-up page
|   |   |   +-- onboarding/page.tsx   <- New user setup wizard
|   |   |   +-- profile/[uid]/        <- Public profile pages
|   |   |   +-- companies/            <- Company directory
|   |   |   +-- admin/page.tsx        <- Super admin panel
|   |   |   +-- candidate/            <- All candidate pages
|   |   |   |   +-- dashboard/        <- Candidate home
|   |   |   |   +-- jobs/             <- Job search & details
|   |   |   |   +-- smart-apply/      <- Automated applications
|   |   |   |   +-- resume-builder/   <- AI resume editor
|   |   |   |   +-- applications/     <- Application tracker
|   |   |   |   +-- interview/        <- Interview tools
|   |   |   |   +-- messages/         <- Chat
|   |   |   |   +-- network/          <- Connections
|   |   |   |   +-- profile/          <- Edit profile
|   |   |   |   +-- settings/         <- API keys, 2FA, theme
|   |   |   +-- recruiter/            <- All recruiter pages
|   |   |       +-- dashboard/        <- Recruiter home
|   |   |       +-- requisitions/     <- Job postings
|   |   |       +-- applications/     <- Application pipeline
|   |   |       +-- candidates/       <- Candidate directory
|   |   |       +-- sourcing/         <- Passive sourcing
|   |   |       +-- messages/         <- Chat
|   |   |       +-- network/          <- Connections
|   |   |       +-- webhooks/         <- ATS integration
|   |   +-- components/               <- Reusable UI pieces
|   |   |   +-- LoginModal.tsx        <- Login / signup popup
|   |   |   +-- Navbar.tsx            <- Top navigation bar
|   |   |   +-- layout/               <- Sidebar & layout wrappers
|   |   +-- contexts/                 <- Global app state
|   |   |   +-- AuthContext.tsx       <- Who is logged in?
|   |   |   +-- FeatureFlagsContext.tsx <- Which features are on?
|   |   |   +-- LoginModalContext.tsx <- Is the login popup open?
|   |   |   +-- ThemeContext.tsx      <- Dark or light mode?
|   |   +-- lib/
|   |       +-- api.ts                <- Frontend API helper functions
|   |       +-- firebase.ts           <- Firebase setup
|   |
|   +-- backend/                      <- The Python server
|   |   +-- app.py                    <- Server entry point
|   |   +-- routes.py                 <- ALL 50+ endpoints (~4000 lines)
|   |   +-- gemini_utils.py           <- AI / Gemini helper functions
|   |   +-- firebase_utils.py         <- Firebase Admin helpers
|   |   +-- vault_utils.py            <- API key encryption/decryption
|   |   +-- file_parser.py            <- PDF/DOCX text extraction
|   |   +-- document_generator.py     <- PDF/DOCX file generation
|   |   +-- job_crawler.py            <- External job board scraping
|   |   +-- email_utils.py            <- Email sending (via Resend API)
|   |   +-- requirements.txt          <- Python packages list
|   |   +-- credentials/              <- [GITIGNORED] Firebase service account
|   |
|   +-- browser-extension/            <- The Chrome plugin
|   |   +-- manifest.json             <- Extension configuration
|   |   +-- popup.html / popup.js     <- Extension UI and its logic
|   |   +-- popup.css                 <- Extension styles
|   |   +-- content.js                <- Form-filling code (injected into pages)
|   |   +-- background.js             <- Background worker (API calls)
|   |   +-- mock_apply_page.html      <- Test page for development
|   |
|   +-- package.json                  <- Node.js dependencies
|
+-- mobile/                           <- The Android / iOS app
|   +-- lib/
|   |   +-- main.dart                 <- App entry point
|   |   +-- api/api_service.dart      <- All API calls (mirrors backend)
|   |   +-- services/auth_service.dart <- Login, logout, Google Sign-In
|   |   +-- auth/login_page.dart      <- Login screen
|   |   +-- auth/signup_page.dart     <- Sign-up screen
|   |   +-- pages/                    <- Every screen in the app (27 screens)
|   |   +-- widgets/                  <- Reusable Flutter components
|   +-- android/app/google-services.json <- Firebase Android config
|   +-- pubspec.yaml                  <- Flutter/Dart dependencies
|
+-- tests/                            <- Automated test suite
|   +-- test_api_health.py            <- Checks backend endpoints respond
|   +-- test_ui_candidate.py          <- Simulates a candidate using the site
|   +-- test_ui_recruiter.py          <- Simulates a recruiter using the site
|   +-- test_ui_public.py             <- Tests public pages
|   +-- test_ai_explorer.py           <- Tests AI features
|   +-- config.py                     <- Test settings (URLs from env vars)
|   +-- conftest.py                   <- Shared test setup
|   +-- create_test_accounts.py       <- Creates Firebase test users
|   +-- requirements.txt              <- Python test packages
|
+-- docs/
|   +-- DOCUMENTATION.md              <- Full documentation (Markdown)
|   +-- CareerCraft_Documentation.tex <- This file (LaTeX)
|   +-- TECHNICAL.md                  <- Deep technical architecture guide
|
+-- firestore.rules                   <- Database security rules
+-- storage.rules                     <- File storage security rules
+-- deploy.ps1                        <- One-command deployment script
+-- .gitignore                        <- Files NOT uploaded to GitHub
+-- README.md                         <- Quick start guide
\end{lstlisting}

% ─────────────────────────────────────────────────────────────
\chapter{Glossary}
% ─────────────────────────────────────────────────────────────

Definitions for every technical term used in this documentation.
Written so that anyone can understand them.

\begin{description}[style=nextline, leftmargin=3cm, labelwidth=2.8cm, font=\bfseries\color{ccpurple}]

\item[API]
A way for two programs to talk to each other.
Like a waiter who takes your order (request) to the kitchen (server) and brings back your food (response).

\item[API Key]
A secret password that lets you use an AI or cloud service.
Like a membership card for a gym --- you show it every time you want to use the facilities.

\item[ATS]
Applicant Tracking System.  Software companies use to automatically filter job applications before a human reads them.
Think of it as a robot that reads your resume first.

\item[ATS Score]
A number (0--100) measuring how likely your resume is to get past the ATS robot filter.
Anything above 70 is generally good.

\item[Authentication]
Proving you are who you say you are.  Logging in is authentication.
The system checks your password to confirm your identity.

\item[Authorization]
Checking whether you are \emph{allowed} to do something after you have already proved who you are.
``You can read this file, but not delete it.''

\item[Backend]
The server --- the part of the app that stores data, runs AI, and enforces rules.
You cannot see it directly, but every action you take in the app triggers a backend request.

\item[BYOK]
Bring Your Own Key.
Instead of paying a subscription, you provide your own free AI API key and \cc{} uses it.

\item[Chrome Extension]
A small program that installs inside the Chrome browser and adds new functionality.
The \cc{} extension adds an autofill button to job application pages.

\item[Cloud Run]
Google's service for running programs on the internet.
It automatically provides more computing power when many people use the app at once (scaling).

\item[Context (React)]
A way to share data between different parts of a website without passing it through every layer.
Like a shared whiteboard that any component can read and write to.

\item[Docker]
Technology that packages a program and everything it needs into a single portable ``container''.
That container runs the same way on any computer or cloud service.

\item[Endpoint]
A specific URL the backend listens to.
Like a specific phone extension for a specific department in a company.

\item[Encryption]
Scrambling data so only the intended recipient can read it.
Like a secret code: \code{HELLO} might become \code{KHOOR} and only someone with the key can decode it.

\item[Fernet]
A specific, industry-standard encryption method used to scramble API keys in the database.

\item[Firebase]
Google's platform for building apps quickly.
It provides a database (Firestore), login system (Auth), and file storage, all managed by Google.

\item[Firestore]
Google's cloud database used by \cc{}.
Data is stored as collections of documents, similar to folders of text files.

\item[Flutter]
Google's framework for building phone apps from a single codebase.
The same code works on both Android and iOS phones.

\item[Frontend]
The part of the app you see and interact with --- the website UI or the phone app screen.

\item[Git]
Software that tracks every change made to code over time.
It lets multiple developers work on the same project without overwriting each other's work.

\item[Gitignore]
A configuration file listing paths that Git should never upload to GitHub.
Used to keep passwords and credentials out of the public code repository.

\item[Google Cloud]
Google's cloud computing platform where this app is hosted.
Think of it as renting space on Google's powerful computers instead of running your own.

\item[Gunicorn]
A Python program that runs Flask in production.
It handles many incoming requests at the same time, unlike the development server which handles only one.

\item[ID Token]
A short-lived digital pass Firebase gives you after you log in.
Your browser sends it with every request to prove you are logged in.
Expires after one hour but is silently refreshed.

\item[Kanban Board]
A visual task management tool using columns (``To Do'' $\to$ ``In Progress'' $\to$ ``Done'').
\cc{} uses it for the applications pipeline.

\item[LLM]
Large Language Model.
The AI technology behind ChatGPT, Gemini, Claude, etc.
Trained on billions of words; can write, explain, reason, and answer questions.

\item[Manifest.json]
A configuration file for Chrome extensions.
Tells Chrome what permissions the extension needs and which scripts to run.

\item[Microservice / API]
A small, self-contained program that does one specific job.
The \cc{} backend is an API that the website, mobile app, and extension all call.

\item[Next.js]
A framework for building fast, modern websites using React.
Handles routing, server-side rendering, and performance automatically.

\item[Node.js]
A program that lets JavaScript code run on a server (not just inside a browser).
The \cc{} website is built and started using Node.js.

\item[OAuth]
A standard way to log in using another service (e.g.\ ``Log in with Google'')
without giving the app your Google password.
The third-party service confirms your identity; the app never sees your password.

\item[Python]
A popular programming language known for being easy to read.
The \cc{} backend is written in Python using the Flask framework.

\item[React]
A JavaScript library for building user interfaces.
The \cc{} web frontend is built with React (via Next.js).

\item[REST API]
A standard style for building APIs.
Different URLs correspond to different actions:
GET = read, POST = create, PATCH = update, DELETE = remove.

\item[Semantic Search]
Search that understands meaning, not just keywords.
``I want a chill remote role'' finds ``Work-from-home positions with flexible hours''.

\item[Vault Master Key]
The server-side secret that locks and unlocks your encrypted API keys.
It is stored only as an environment variable on the Cloud Run server --- never in any code file.

\item[Webhook]
A way for one app to automatically notify another app when something happens.
Like a push notification from one system to another: ``Hey, a new application just arrived!''

\end{description}

% ─────────────────────────────────────────────────────────────
\vfill
\begin{center}
  \textcolor{graytext}{\small
    CareerCraft Documentation $\cdot$ Version 1.0 $\cdot$ July 2026 \\
    Built with Next.js 15 $\cdot$ Flutter $\cdot$ Flask $\cdot$ Firebase $\cdot$ Google Cloud Run\\[4pt]
    \url{https://github.com/Sree8778/CareerCraft}
  }
\end{center}

\end{document}
